Understanding and Verifying the Shape of Stencil Computations

### 2017-03-25 oopsla17/lattice-model.tex
forgotten part of the proof

@@

\begin{proof}
  We show soundness for each of the equivalences.
  \begin{description}
    \item[Basic] These follow from basic properties of lattices.
%
    \item[Dist] This is immediate from the definition of distributive
      lattice which the model is one.
%
    \item[Overlapping pointed] Let $\interp{\textcap{n}}$ be $n$. Counterparts
      of individual regions for some Boolean $p$ are given below:
%
      \begin{align*}
        \interp{\texttt{\textcap{R}(depth=\textcap{k},dim=\textcap{n},\_)}}_N
        & = \vecgen{N}{n}{\interv{-k}{k}{p}} \\
%
        \interp{\texttt{pointed(dim=\textcap{n})}}_N
        &= \vecgen{N}{n}{\interv{0}{0}{\textsf{true}}} \\
%
        \interp{\texttt{\textcap{R}(depth=\textcap{k},dim=\textcap{n})}}_N
        &= \vecgen{N}{n}{\interv{-k}{k}{\textsf{true}}}
      \end{align*}

@@

    \item[Point] Let $\interp{\textcap{R}^{\textnormal{\textit{p}}}}_N$ and
      $\interp{\textcap{S}^{\textnormal{\textit{p'}}}}_N$ be
      $\vecgen{N}{k}{\interv{a}{b}{p}}$ and $\vecgen{N}{l}{\interv{c}{d}{p'}}$
      respectively for some $a$ and $c$ less than or equal to 0, for some $c$
      and $d$ greater than or equal to 0, for some indices $k$ and $l$ be
      $\interp{\textcap{dr}}$ and $\interp{\textcap{ds}}$, which are not
      necessarily distinct and $p$ and $p'$ are \textsf{true} if pointed and
      \textsf{false} otherwise.
%
      \begin{align*}
        \hspace{2em&\hspace{-2em}}
        \interp
          {{(\textcap{R}^{\textit{t}} * \textcap{S}^{\textit{f}})}
           \;\texttt{+}\;
           {(\textcap{R}^{\textit{f}} * \textcap{S}^{\textit{t}})}
           \;\texttt{+}\;
           \texttt{pointed(dim=\textcap{dr})*pointed(dim=\textcap{ds})}}_N \\
        & = {(\interp{\textcap{R}^{\textit{t}}}_N \cap
              \interp{\textcap{S}^{\textit{f}}}_N)} \cup
            {(\interp{\textcap{R}^{\textit{f}}}_N \cap
              \interp{\textcap{S}^{\textit{t}}}_N)} \;\cup \\
        & \quad\,\, {(\vecgen{N}{\interp{ds}}{\interv{0}{0}{\textsf{true}}}
                      \;\cup\;
                      \vecgen{N}{\interp{dr}}{\interv{0}{0}{\textsf{true}}})} \\
        & = \{ x \mid
            \bigwedge_{\substack{1 \leq i \leq N \\ i \neq k \neq l}} x_i \in
              \interv{\infty}{\infty}{\textsf{true}}
            \wedge a \leq x_k \leq b
            \wedge {(c \leq x_l \leq d \wedge x_l \neq 0)} \} \;\cup \\
        & \quad\,\, \{ x \mid
            \bigwedge_{\substack{1 \leq i \leq N \\ i \neq k \neq l}} x_i \in
              \interv{\infty}{\infty}{\textsf{true}}
            \wedge {(a \leq x_k \leq b \wedge x_k \neq 0)}
            \wedge c \leq x_l \leq d \} \;\cup \\
        & \quad\,\, \{ x \mid
            \bigwedge_{\substack{1 \leq i \leq N \\ i \neq k \neq l}} x_i \in
              \interv{\infty}{\infty}{\textsf{true}}
            \wedge (x_k = 0 \wedge x_l = 0) \} \\
        & = \{ x \mid
            \bigwedge_{\substack{1 \leq i \leq N \\ i \neq k \neq l}} x_i \in
              \interv{\infty}{\infty}{\textsf{true}}
            \wedge a \leq x_k \leq b
          \wedge c \leq x_l \leq d \wedge {(x_k \neq 0 \vee x_l \neq 0)} \}
          \;\cup \\
        & \quad\,\, \{ x \mid
            \bigwedge_{\substack{1 \leq i \leq N \\ i \neq k \neq l}} x_i \in
              \interv{\infty}{\infty}{\textsf{true}}
            \wedge (x_k = 0 \wedge x_l = 0) \} \\
        & = \{ x \mid
            \bigwedge_{\substack{1 \leq i \leq N \\ i \neq k \neq l}} x_i \in
              \interv{\infty}{\infty}{\textsf{true}}
            \wedge a \leq x_k \leq b
            \wedge c \leq x_l \leq d \} \\
        & = \textcap{R}^{\textit{t}} \texttt{*} \textcap{S}^{\textit{t}}
      \end{align*}
  \end{description}
\end{proof}

>>>>

We define an equivalence relation, $\equiv$, on regions as follows:

@@

\begin{proof}
  Both $\equiv$ and $=$ are equivalence relations. We only need to show that
  each property associated with specifications equivalence holds as an equality
  in the model.
%
  \begin{description}
    \item[Basic] These follow from basic properties of lattices.
%
    \item[Dist] This is immediate from the definition of distributive
      lattice which the model is one.
%
    \item[Overlapping pointed] Let $\interp{\textcap{n}}$ be $n$. Counterparts
      of individual regions for some Boolean $p$ are given below:
%
      \begin{align*}
        \interp{\texttt{\textcap{R}(depth=\textcap{k},dim=\textcap{n},\_)}}_N
        & = \vecgen{N}{n}{\interv{-k}{k}{p}} \\
%
        \interp{\texttt{pointed(dim=\textcap{n})}}_N
        &= \vecgen{N}{n}{\interv{0}{0}{\textsf{true}}} \\
%
        \interp{\texttt{\textcap{R}(depth=\textcap{k},dim=\textcap{n})}}_N
        &= \vecgen{N}{n}{\interv{-k}{k}{\textsf{true}}}
      \end{align*}

@@

    \item[Point] We will prove the first equivalence and then use that to prove
      the second.
%
      Let $\interp{\textcap{R}^{\textnormal{\textit{p}}}}_N$ and
      $\interp{\textcap{S}^{\textnormal{\textit{p'}}}}_N$ be
      $\vecgen{N}{k}{\interv{a}{b}{p}}$ and $\vecgen{N}{l}{\interv{c}{d}{p'}}$
      respectively for some $a$ and $c$ less than or equal to 0, for some $c$
      and $d$ greater than or equal to 0, for some indices $k$ and $l$ be
      $\interp{\textcap{dr}}$ and $\interp{\textcap{ds}}$, which are not
      necessarily distinct and $p$ and $p'$ are \textsf{true} if pointed and
      \textsf{false} otherwise.
%
      \begin{align*}
        \hspace{2em&\hspace{-2em}}
        \interp
          {{(\textcap{R}^{\textit{t}} * \textcap{S}^{\textit{f}})}
           \;\texttt{+}\;
           {(\textcap{R}^{\textit{f}} * \textcap{S}^{\textit{t}})}
           \;\texttt{+}\;
           \texttt{pointed(dim=\textcap{dr})*pointed(dim=\textcap{ds})}}_N \\
        & = {(\interp{\textcap{R}^{\textit{t}}}_N \cap
              \interp{\textcap{S}^{\textit{f}}}_N)} \cup
            {(\interp{\textcap{R}^{\textit{f}}}_N \cap
              \interp{\textcap{S}^{\textit{t}}}_N)} \;\cup \\
        & \quad\,\, {(\vecgen{N}{\interp{ds}}{\interv{0}{0}{\textsf{true}}}
                      \;\cup\;
                      \vecgen{N}{\interp{dr}}{\interv{0}{0}{\textsf{true}}})} \\
        & = \{ x \mid
            \bigwedge_{\substack{1 \leq i \leq N \\ i \neq k \neq l}} x_i \in
              \interv{\infty}{\infty}{\textsf{true}}
            \wedge a \leq x_k \leq b
            \wedge {(c \leq x_l \leq d \wedge x_l \neq 0)} \} \;\cup \\
        & \quad\,\, \{ x \mid
            \bigwedge_{\substack{1 \leq i \leq N \\ i \neq k \neq l}} x_i \in
              \interv{\infty}{\infty}{\textsf{true}}
            \wedge {(a \leq x_k \leq b \wedge x_k \neq 0)}
            \wedge c \leq x_l \leq d \} \;\cup \\
        & \quad\,\, \{ x \mid
            \bigwedge_{\substack{1 \leq i \leq N \\ i \neq k \neq l}} x_i \in
              \interv{\infty}{\infty}{\textsf{true}}
            \wedge (x_k = 0 \wedge x_l = 0) \} \\
        & = \{ x \mid
            \bigwedge_{\substack{1 \leq i \leq N \\ i \neq k \neq l}} x_i \in
              \interv{\infty}{\infty}{\textsf{true}}
            \wedge a \leq x_k \leq b
          \wedge c \leq x_l \leq d \wedge {(x_k \neq 0 \vee x_l \neq 0)} \}
          \;\cup \\
        & \quad\,\, \{ x \mid
            \bigwedge_{\substack{1 \leq i \leq N \\ i \neq k \neq l}} x_i \in
              \interv{\infty}{\infty}{\textsf{true}}
            \wedge (x_k = 0 \wedge x_l = 0) \} \\
        & = \{ x \mid
            \bigwedge_{\substack{1 \leq i \leq N \\ i \neq k \neq l}} x_i \in
              \interv{\infty}{\infty}{\textsf{true}}
            \wedge a \leq x_k \leq b
            \wedge c \leq x_l \leq d \} \\
        & = \interp{\textcap{R}^{\textit{t}} \texttt{*} \textcap{S}^{\textit{t}}}_N
      \end{align*}
%
      Now we prove the second equivalence:
      \begin{align*}
        \hspace{2em}&\hspace{-2em} \interp{
          (\textcap{R}^{\textit{t}} \texttt{+} \textcap{S}^{\textit{f}})
          \texttt{*}
          (\textcap{R}^{\textit{f}} \texttt{+} \textcap{S}^{\textit{t}})
        }_N \\
        &= \interp{
             (\textcap{R}^{\textit{t}} \texttt{*} \textcap{R}^{\textit{f}})
             \texttt{+}
             (\textcap{S}^{\textit{t}} \texttt{*} \textcap{S}^{\textit{f}})
             \texttt{+}
             (\textcap{R}^{\textit{t}} \texttt{*} \textcap{S}^{\textit{t}})
             \texttt{+}
             (\textcap{R}^{\textit{f}} \texttt{*} \textcap{S}^{\textit{f}})
           }_N \\
        &= \interp{
             \textcap{R}^{\textit{f}}
             \texttt{+}
             \textcap{S}^{\textit{f}}
             \texttt{+}
             (\textcap{R}^{\textit{t}} \texttt{*} \textcap{S}^{\textit{t}})
           }_N \\
        &= \interp
             {\textcap{R}^{\textit{f}}
              \texttt{+}
              \textcap{S}^{\textit{f}}
              \texttt{+}
              {(\textcap{R}^{\textit{t}} \texttt{*} \textcap{S}^{\textit{f}})}
               \;\texttt{+}\;
               {(\textcap{R}^{\textit{f}} \texttt{*} \textcap{S}^{\textit{t}})}
               \;\texttt{+}\;
               \texttt{pointed(dim=\textcap{dr})*pointed(dim=\textcap{ds})}}_N \\
        &= \interp{\textcap{R}^{\textit{f}} \texttt{+} \textcap{S}^{\textit{f}}
                   \;\texttt{+}\;
                   \texttt{pointed(dim=\textcap{dr})*pointed(dim=\textcap{ds})}}_N
      \end{align*}
  \end{description}
\end{proof}
